Secure Composition of Robust and Optimising Compilers

### 2023-07-05 popl/main.tex
some in 2.2

\MPin{
	classes?
}
\subsection{Secure Compilers}\label{subsec:bg:rtp}

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.
For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.
It is considered good if this translation is semantics-preserving, i.e., correct.
Correct compilers may still be insecure compilers\MK{citation needed}.
Programs translated by insecure compilers may violate security properties that were assumed to hold, given the presence of a context--level program.
So, ideally, a compiler is secure~\cite{abate2019jour} in the sense of the following definition:

@@

>>>>

\MPin{
	classes?
	% 
}
Classes of properties can be used to state whether a compiler is correct, or even secure so now we turn to the definition of (secure) compilers.

\subsection{Secure Compilers}\label{subsec:bg:rtp}

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.\MP{good sentence}
For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.\MP{not a fan of this sentence}
It is considered good if this translation is semantics-preserving, i.e., correct. \MP{passive}
Correct compilers may still be insecure compilers\MK{citation needed}.
Programs translated by insecure compilers may violate security properties that were assumed to hold, given the presence of a context--level program.
So, ideally, a compiler is secure~\cite{abate2019jour} in the sense of the following definition:
\MPin{does not really flow.
% 
start with compilers (as now),
then: for a compiler to be correct we expect ... ... (no def)
then: for a compiler to be secure we use the robust compilation framework of ... that says ... ... def
}

@@

\MPin{
	again, hybrid definition.
	keep one version.
	i suggest: text outside (typically before the def, in the text leading to it), formalism inside
}
